Marlowe: implementing and analysing financial contracts on blockchain

### 2019-12-10 papers/marlowe2019/paper.tex
More changes

Let us say that Alice has 1000 Lovelace on her account, and Bob wants to receive the payment.
The payment could be obtained only after \emph{When} has timed out after slot 200.
Buy if we evaluate the contract after slot 200, \emph{If} reduces to \emph{Close}, and
Bob will not receive the payment. So he must evaluate the contract before slot 100 to
reduce \emph{If} to \emph{When}.
To do that he can spend the contract transaction output with empty list of inputs in \emph{redeemer}.
He should then do the same after slot 200 to receive the payment.

@@

The Marlowe validator script checks that a transaction contains a valid continuation
output in case a contract is not closed, by checking the hash of the output validator and state.
The continuation must have the same validator, hence the same hash of the validator script.
It should contain both the expected continuation contract and the state, evaluated by the \emph{computeTransaction}
function.

@@

When a contract evaluates to \emph{Close}, all remaining balances must payed out
to respective owners, removing the contract from the set of unspent transaction outputs.

@@

Simple token creation gives interesting possibilities of representing Marlowe contract parties by tokens.
Currently parties are represented as public keys. We expect a valid signature for each input,
and make payments to  addresses for the public key of a party.
In similar matter, we could check proofs of ownership of a particular token.

This allows us to tokenize contract participants, and abstract away concrete public keys into contract \emph{roles}.
Thus, those roles could be traded independently of a contract.
Also, we can represent a role with multiple \emph{shares}, allowing automatic distribution of a payment
proportionally to a number of shares owned.

>>>>

Let us say that Alice has 1000 Lovelace on her account, and Bob wants to receive the payment.
The payment could be obtained only after \emph{When} has timed out after slot 200.
But if we evaluate the contract after slot 200, \emph{If} reduces to \emph{Close}, and
Bob will not receive the payment. So he must evaluate the contract before slot 100 to
reduce \emph{If} to \emph{When}.
To achieve that, Bob must spend the contract transaction output with an empty list of inputs in the \emph{Redeemer}.
He can then do the same after slot 200 to receive the payment.

@@

Except for the transaction that closes a Marlowe contract, the Marlowe validator script checks that a spending transaction contains a valid continuation
output, i.e: the hash of the output validator is the same (same hash), and the new state and contract are the expected ones: the ones resulting from applying the \emph{computeTransaction} to the given inputs.

@@

When a contract evaluates to \emph{Close}, all remaining balances the accounts of the contract are payed out
to the respective owners of each account, and the contract is removed from the set of unspent transaction outputs.

@@

Simple token creation gives interesting possibilities of representing Marlowe contract parties by tokens.
Currently parties are represented as public keys. We expect a valid signature for each input,
and make payments to addresses for the public key of a party.
Analogously, we could instead check proofs of ownership of a particular token.

This would allows us to tokenize contract participants, and abstract away concrete public keys into contract \emph{roles}.
In turn, those roles could be traded independently of a contract.
Additionally, we can split a role in multiple \emph{shares}, which would allow automatic distribution of a payment
proportionally to the number of shares owned.
